---
title: "Week 2 Quiz"
author: "Bruno H M Oliveira"
date: "28/12/2019"
output: html_document
---


Question 1 
---

```{R}
cube <- function(x, n){
  x^3
}

cube(3)
```
> OUTPUT: 27

Question 2
---

```{R}
x <- 1:10

if(x > 5){
  x <- 0
}
```
> A: 'x' is a vector of length 10 and 'if' can only test a single logical statement.

Question 3
---

```{r}
f <- function(x) {
  g <- function(y) {
    y + z
  }
  z <- 4
  x + g(x)
}

z <- 10
f(3)
```
> OUTPUT: 10

Question 4
---

```{r}
x <- 5
y <- if(x < 3) {
  NA
} else {
  10
}
y
```
> OUTPUT: 10


Question 5
---

```{r}
h <- function(x, y = NULL, d = 3L) {
  z <- cbind(x, d)
  if(!is.null(y))
    z <- z + y
  else
    z <- z + f
  g <- x + y / z
  if(d == 3L)
    return(g)
  g <- g + 10
  g
}
```
> f <- free variable 

Question 6
---

#### What is an environment in R?
> A: Collection of symbols, values pairs

Question 7 
---

#### The R language uses what type of scoping rule for resolving free variables?
> A: Lexical Scope

Question 8
---

#### How are free variables in R functions resolved?
> A: The values of free variables are searched for in the environment in wich the function was defined.
